---
title: "Data Science for Public Policy"
subtitle: "Final Project"
author: "Xiangming Zeng - xz634, Ruiyang Zhang - rz326, Lingxi Li - ll1188, Xiaorui Shi - xs215"
execute:
  warning: false
format:
  html:
    embed-resources: true
---

# Research question

In the current study, we aim to explore and analyze the distribution of new energy power production and its power stations at the county level in the United States for the year 2021, using DC charging stations as a case study to further examine the relationship between charging infrastructure and public facilities. By integrating and utilizing data from the American Community Survey (ACS), such as income, education level, heating methods, and commuting methods, we will predict the number of charging stations in each county. Additionally, we will assess the air quality forecasts for each county and how these forecasts reflect the investments in new energy sources in 2023. This study not only provides insights into the geographic distribution of new energy technologies but also supports future energy policies and infrastructure development through an analysis of the interaction between charging infrastructure and socio-economic factors.

## Data sets description


## Library packages

```{r}
library(tidyverse)
library(sf)
library(here)
library(tigris)
library(tidycensus)
library(readxl)
library(here)
library(purrr)
library(tidymodels)
library(vip)
```

## Overview: green electricity generation in the U.S.

### Read and combine datasets

```{r}
#read electric power plants data
plants <- read_excel("data/2___Plant_Y2021.xlsx", skip=1) %>% 
  janitor::clean_names() %>% 
  select(plant_code, latitude, longitude)

#read electricity generation data
elec_generation <- read_excel("data/EIA923_Schedules_2_3_4_5_M_12_2021_Final_Revision.xlsx", 
                         sheet = 1, skip = 5) %>% 
  janitor::clean_names() %>% 
  mutate(plant_code = plant_id,
         fuel_type = aer_fuel_type_code,
         net_generation = net_generation_megawatthours) %>% 
  select(plant_code, fuel_type, net_generation) 

#combine datasets
elec_generation <- left_join(x = elec_generation,y = plants,by = "plant_code") %>% 
  filter(
    !is.na(longitude),
    !is.na(latitude)
  ) %>% 
  st_as_sf(coords = c("longitude","latitude")) %>% 
  st_set_crs(4326) 
```

### County-level distribution of green electricity generation

```{r}
#filter green electricity generation
green_elec_generation <- elec_generation %>% 
  filter(fuel_type %in% c("SUN","GEO","HPS","HYC","MLG","ORW","WND","WWW"))

#read counties data
counties <- counties(cb = TRUE, progress_bar = FALSE) %>%
  janitor::clean_names() %>% 
  st_transform(crs = 4326) %>%
  filter(!(stusps %in% c("PR", "GU", "MP", "VI", "HI", "AK", "AS"))) %>% 
  select(geoid, name, stusps, state_name, geometry)

#use spatial join to get green electricity generated in each county
c_green_elec <- st_join(counties, green_elec_generation) %>% 
  st_drop_geometry() %>% 
  group_by(geoid) %>% 
  summarize(green_elec = sum(net_generation)) %>% 
  mutate(green_elec = replace_na(green_elec, 0))

#combine datasets to get geometry for c_green_elec
c_green_elec <- left_join(counties, c_green_elec, by = "geoid")

#visualize green electricity generation at county-level
ggplot()+
  geom_sf(c_green_elec, mapping = aes(fill = log(green_elec)))+ 
  scale_fill_gradient(
    low = "lightgreen",
    high = "darkgreen",
    na.value = "lightyellow"
  )+
  labs(title = "Net Renewable Electricity Generation By County",
       subtitle = "logged megawatthours (white indicates zero generation)",
       caption = "U.S. Energy Information Administration",
       fill = "") +
  theme_void()
```

From the graph, we can see that green electricity production is mainly distributed along the East Coast, the West, and the Northeast in the United States, while it is relatively lacking in the center.

### State-level distribution of green electricity generation

```{r}
s_green_elec <- c_green_elec %>% 
  st_drop_geometry() %>% 
  group_by(stusps) %>% 
  summarise(green_elec = sum(green_elec))

#read states data
states <- states(cb = TRUE, progress_bar = FALSE) %>% 
  janitor::clean_names() %>% 
  st_transform(crs = 4326) %>%
  filter(!(stusps %in% c("PR", "GU", "MP", "VI", "HI", "AK", "AS"))) %>% 
  select(stusps, geometry)

#combine datasets to get geometry for s_green_elec
s_green_elec <- left_join(states, s_green_elec, by = "stusps")

#filter plants with green electricity generation within states
green_elec_generation <- st_filter(green_elec_generation, states)

#identify 3 most common fuel type
green_elec_generation %>% 
  group_by(fuel_type) %>% 
  summarise(n = n()) %>% 
  arrange(n)

#visualize green electricity generation at state-level
ggplot()+
  geom_sf(s_green_elec, mapping = aes(fill = green_elec/1000))+ 
  scale_fill_gradient(
    low = "lightgreen",
    high = "darkgreen"
  )+
  geom_sf(data = green_elec_generation %>% 
            filter(fuel_type %in% c("HYC", "SUN", "WND")),
          mapping = aes(color = fuel_type), size=0.3)+
  labs(title = "Net renewable electricity generation by state",
       subtitle = "1000 megawatthours",
       caption = "U.S. Energy Information Administration",
       fill = "",
       color = "plants with green electricity generation") +
  scale_color_manual(
    name = "Fuel Type",
    labels = c("HYC" = "Hydroelectric Conventional", "SUN" = "Solar", "WND" = "Wind"),
    values = c("HYC" = "red", "SUN" = "yellow", "WND" = "blue")) +
  theme_void()
```

From the graph, we can see that California, Washington, and Texas are leading in green electricity production. Additionally, power plants of different energy types have distinct spatial distribution characteristics. Solar energy is mainly concentrated on the East and West Coasts, wind energy is mainly concentrated in the central inland areas, while the distribution of hydroelectric conventional is more dispersed.

```{r}
#remove used dataframes
rm(green_elec_generation, plants, s_green_elec)
```

## A micro case: alternative fueling stations in DC

### Read and combine datasets

```{r}
#read all datasets
dc_roads <- roads(state = "DC", 
                  county = "District of Columbia") %>% 
  st_transform(crs = 4269)

dc_income <- get_acs(
  geography = "tract",
  variables = "B19013_001",
  state = "DC",
  county = "District of Columbia",
  geometry = TRUE,
  year = 2021,
  progress = FALSE
)

dc_hospitals <- st_read("data/DC_Hospitals.geojson") %>% 
  st_transform(crs = 4326) %>% 
  select(geometry) %>% 
  mutate(facility = "Hospital")

dc_cha_schs <- st_read("data/DC_Charter_Schools.geojson") %>% 
  st_transform(crs = 4326) %>% 
  select(geometry) %>% 
  mutate(facility = "Charter School")

dc_pub_schs <- st_read("data/DC_Public_Schools.geojson") %>% 
  st_transform(crs = 4326) %>% 
  select(geometry) %>% 
  mutate(facility = "Public School")

dc_campuses <- st_read("data/University_and_College_Campuses.geojson") %>% 
  st_transform(crs = 4326) %>% 
  select(geometry) %>% 
  mutate(facility = "University/College Campus")

dc_gov <- st_read("data/District_Government_Owned_Structures.geojson") %>% 
  st_transform(crs = 4326) %>% 
  select(geometry) %>% 
  mutate(facility = "Governmental Building")

alt_fuel_stations <- st_read("data/Alternative_Fueling_Stations.geojson") %>% 
  st_transform(crs = 4326) %>% 
  select(geometry) %>% 
  mutate(facility = "Alternative Fueling Station")

dc_boundary <- states(cb = TRUE, progress_bar = FALSE) %>%
  filter(STUSPS == "DC") %>% 
  st_transform(crs = 4326)

#filter alternative fueling stations in DC
dc_alt_fuel_stations <- st_filter(alt_fuel_stations, dc_boundary) 

#combine datasets
facilities <- bind_rows(dc_hospitals, 
                        dc_cha_schs, 
                        dc_pub_schs, 
                        dc_campuses, 
                        dc_gov,
                        dc_alt_fuel_stations) 
```

### Data visualization

```{r}
#mapping facilities
ggplot()+
  geom_sf(data = dc_income, aes(fill = estimate), color = "white", size = 0)+
  geom_sf(data = dc_roads, color = "orange", alpha = 0.3)+
  geom_sf(data = facilities, aes(color = facility), fill = "white", alpha = 0.7)+
  scale_fill_gradient(
    labels = scales::dollar
  )+
  scale_color_manual(values = c(
    "Alternative Fueling Station" = "green", 
    "Charter School" = "yellow", 
    "Governmental Building" = "grey",
    "Hospital" = "red",
    "Public School" = "gold",
    "University/College Campus" = "pink"
  ))+
  geom_sf(data = dc_campuses, color = "pink", fill = "pink", alpha = 0.5)+
  theme_void()+
  labs(
    title = "The Map of Alternative Fueling Stations In DC",
    subtitle = "Who have poor accessibility to alternative fueling stations?",
    caption = "U.S. Department of Transportation",
    fill = "Household Income",
    color = "Facilities") 
```

From the map, we can see that alternative fueling stations are concentrated in the downtown area of DC, while outside the downtown area, they are mainly clustered along the main roads.

University campuses generally have good accessibility to alternative fueling stations. Hospitals in the northern part of DC are all near alternative fueling stations, while the three hospitals in the south are relatively far from them.

In the northwest of DC, where the household income is the highest, the distribution of alternative fueling stations is relatively even, and residents and schools have good accessibility to them.

In the northeast of DC, although the household income is lower, the distribution of alternative fueling stations is still relatively even.

In the eastern part, where the household income further decreases, despite the presence of numerous schools and government buildings, there are only few and concentrated alternative fueling stations, resulting in poor accessibility.

In the southern part, where the household income is low and there are many schools, hospitals, and government buildings, the number of alternative fueling stations is few and mainly located along the main roads, leading to poor accessibility.

Overall, alternative fueling stations are concentrated in the downtown area of DC, and the household income of neighborhoods is highly correlated with the accessibility of alternative fueling stations. Groups with disadvantaged socio-economic status face difficulties in accessing new energy charging facilities.

```{r}
#remove used dataframes
rm(dc_boundary,
   dc_income,
   dc_roads,
   dc_hospitals, 
   dc_cha_schs, 
   dc_pub_schs, 
   dc_campuses, 
   dc_gov,
   dc_alt_fuel_stations,
   facilities)
```

## Combine datasets for machine learning

### Combine existing data

```{r}
# count the number of alternative fueling stations in each county
c_fueling_stations <- st_join(counties, alt_fuel_stations) %>% 
  st_drop_geometry() %>% 
  group_by(geoid) %>% 
  summarize(alt_fuel_stations = n())

# sum the total electricity generation in each county
c_total_elec <- st_join(counties, elec_generation) %>% 
  st_drop_geometry() %>% 
  group_by(geoid) %>% 
  summarize(total_elec = sum(net_generation)) %>% 
  mutate(total_elec = replace_na(total_elec, 0))

#combine all county-level datasets
green <- left_join(c_green_elec, c_total_elec, by = "geoid")
green <- left_join(green, c_fueling_stations, by = "geoid")
```

### Combine air quality data

```{r}
#read air quality index data 
c_aqi <- read.csv("data/annual_aqi_by_county_2021.csv") %>% 
  janitor::clean_names() %>% 
  select(state, county, days_with_aqi, good_days) %>% 
#use the percent of good days to indicate air quality
  mutate(good_days_rate = 100*good_days/days_with_aqi) %>% 
  select(state, county, good_days_rate)

#combine datasets
green <- left_join(green, c_aqi, by = c("state_name" = "state", "name" = "county"))
```

### Combine urban categories data

```{r}
#read urban categories data
c_urban <- read.csv("data/Urban-Rural Classification Scheme 2013.csv") %>% 
  janitor::clean_names() %>% 
  select(abb, county, urban = code_2013) %>% 
#reverse coding, using 1-6 to represent increasing urban rate
  mutate(urban = 7 - urban)

#combine datasets
green <- left_join(green, c_urban, by = c("stusps" = "abb", "name" = "county"))
```

### Combine ACS data

```{r}
#create a function
acs_combine <- function(variable, name) {
df <- get_acs(
    geography = "county",
    variables = variable,
    year = 2021,
    progress = FALSE
  ) %>% 
    janitor::clean_names() %>% 
    select(geoid, {{ name }} := estimate) 

green <<- left_join(green, df, by = "geoid")

invisible()
}

#create a list for new acs variables
variables <- list(
  variable = c("B19013_001", 
               "B01003_001",
               "B15003_022E",
               "B08007_001E",
               "B25040_002E",
               "B25040_003E",
               "B25040_004E",
               "B25040_005E",
               "B25040_006E",
               "B25040_007E",
               "B08301_003E",
               "B08301_004E",
               "B08301_010E",
               "B08301_016E",
               "B08301_017E",
               "B08301_018E",
               "B08301_019E"
               ),
  name = c("income", 
           "population", 
           "bachelor",
           "labor",
           "utility_gas",
           "bottled_gas",
           "electricity",
           "oil",
           "coal",
           "wood",
           "drive_alone",
           "carpooled",
           "public_trans",
           "taxicab",
           "motorcycled",
           "bicycled",
           "walked"
          )
)

#combine
pmap(variables, acs_combine)
```

### Remove irrelevant features

```{r}
#remove irrelavant variables
green <- green %>% 
  select(-geoid, -name, -stusps, -state_name) %>% 
  st_drop_geometry()

#remove used datasets
rm(alt_fuel_stations,
   c_aqi,
   c_fueling_stations,
   c_green_elec,
   c_total_elec,
   c_urban,
   elec_generation,
   variables)
```

## Can green energy industry help predict air quality?

Since green energy use (alternative energy cars) and production (green electricity) are more environmental-friendly, we expect that green energy industry contributes to better air quality. In this section, we will use a decision tree model to test this hypothesis.

### Data cleaning 

```{r}
#remove rows with missing air quality
air <- green %>% filter(!is.na(good_days_rate))

#turn good_days_rate into dummy
summary(air$good_days_rate)
```

### Dummy variable generation

The median of good_days_rate is 84, so I will code air_quality as "good" if good_days_rate > 84, and as "bad" if good_days_rate <= 84

```{r}
air <- air %>% 
  mutate(air_quality = if_else(good_days_rate > 84, "good", "bad")) %>%
  mutate(air_quality = factor(air_quality, levels = c("good", "bad"))) %>% 
  select(-good_days_rate)
```

### Decision tree model

```{r}
set.seed(20240511)

#split data
air_split <- initial_split(data = air, prop = 0.75)

air_train <- training(x = air_split)
air_test <- testing(x = air_split)

#create a recipe
air_rec <-
  recipe(formula = air_quality ~ ., data = air_train)

#create a model
air_mod <-
  decision_tree() %>%
  set_engine(engine = "rpart") %>%
  set_mode(mode = "classification")

air_wf <- workflow() %>%
  add_recipe(air_rec) %>%
  add_model(air_mod)

#fit the model
air_fit <- air_wf %>%
  fit(data = air_train)
```

### Evaluate model

```{r}
#evaluate model
predictions <- bind_cols(
  air_test,
  predict(object = air_fit, new_data = air_test),
  predict(object = air_fit, new_data = air_test, type = "prob")
)

#confusion matrix
conf_mat(data = predictions,
         truth = air_quality,
         estimate = .pred_class)

#accuracy
accuracy(data = predictions,
         truth = air_quality,
         estimate = .pred_class)

#precision
precision(data = predictions,
         truth = air_quality,
         estimate = .pred_class)

#recall
recall(data = predictions,
          truth = air_quality,
          estimate = .pred_class)

#feature importance
air_fit %>%
  extract_fit_parsnip() %>%
  vip(num_features = 10)
```

In this prediction result, accuracy, precession, and recall are between 0.6 and o.7, indicating weak prediction power. Therefore, this model can't predict air quality well. Besides, The 10 most important predictors donn't include green_elec or alt_fuel_stations, suggesting that green industry is not a strong predictor for air quality.

### Remove irrelevant data

```{r}
rm(air,
   air_fit,
   air_mod,
   air_rec,
   air_split,
   air_test,
   air_train,
   air_wf,
   predictions)
```

## What's the key predictors for alternative fueling stations?

With the development of the green energy car industry, the demand for alternative fueling stations is increasing. Is there a shortage of alternative fueling stations in DC? To address this question, we will establish a lasso regression model to identify the most significant predictors for the number of alternative fueling stations in a city. We believe this model will be highly relevant for policymakers in urban areas.

### Data cleaning
Due to more than 2000 missing values in good_days_rate, I will remove it to avoid having too small of a sample size.

```{r}
green <- green %>% 
  select(-good_days_rate)
```

### Lasso regression model

```{r}
#split data

green_split <- initial_split(green, prop = 0.75)

green_train <- training(green_split)
green_test <- testing(green_split)

#create a recipe
green_rec <- recipe(alt_fuel_stations ~ . , data = green_train) %>% 
  step_filter_missing(all_predictors()) %>% 
  step_normalize(all_numeric_predictors()) %>% 
  step_impute_median(all_numeric_predictors(), all_nominal_predictors())

#create a lasso model
lasso_green <- linear_reg(penalty = tune(), mixture = 1) %>%
  set_engine("glmnet") %>%
  set_mode("regression")

folds <- vfold_cv(green_train, v = 10, strata = alt_fuel_stations)

lasso_grid <- grid_regular(penalty(), levels = 10)

lasso_wf_green <- workflow() %>% 
  add_recipe(green_rec) %>% 
  add_model(lasso_green)

#fit model
lasso_res_green <- lasso_wf_green %>% 
  tune_grid(resample = folds,
            grid = lasso_grid,
            metrics = metric_set(mae,rmse))

#visualize model fit
lasso_res_green %>% 
  collect_metrics(summarize=F) %>% 
  filter(.metric=="rmse") %>% 
  ggplot(aes(x=id,y=.estimate, group=penalty, color=penalty),alpha=0.5)+
  geom_line()+
  geom_point()+
  theme_minimal()
```

### Evaluate model

```{r}
#select best model
lasso_best_green <-lasso_res_green %>%
  select_best(metric = "rmse")

#finalize model
lasso_final_green <- finalize_workflow(
  lasso_wf_green,
  parameters = lasso_best_green) %>% 
  fit(data = green_train)

#predict
predictions <- bind_cols(
  green_test,
  predict(object = lasso_final_green, new_data = green_test))

#calculate rmse
rmse(data = predictions, truth = alt_fuel_stations, estimate=.pred)

summary(green$alt_fuel_stations)
```

The RMSE is 34, which is relatively small compared to the range of 4783. However, considering the median number of alternative fueling stations is 4, and since most counties are not urban areas, this model will be more applicable in large cities where the number of alternative fueling stations is significantly higher.

```{r}
#feature inportance
lasso_final_green %>%
  extract_fit_parsnip() %>%
  vip(num_features = 10)
```

The four most significant predictors are population, utility gas consumption, population with Bachelor's degree, and electricity consumption. All of these variables have a clear correlation with the demand for alternative fueling stations. Additionally, the remaining key, albeit less significant, factors are primarily related to modes of transportation, indicating that citizens' preferences for cleaner transportation methods such as public transportation, cycling, motorcycling, and walking are also relevant to their demand for alternative fueling stations.